### 2019-06-06 dmtcs_submission.d/intro.tex
ssr: creating the version for DMTCS

\IEEEPARstart{R}{search} on the symmetry properties of Boolean
functions has received a lot of attention from the
logic design and automated synthesis communities. 
(Additional discussion on this is provided in Section~\ref{sse:related}.)
In this paper, we focus on the symmetry properties of
a class of Boolean functions (called \textbf{nested canalyzing functions})
which are used to model biological phenomena.
To define this class, we start with a simpler
class of functions, called \textbf{canalyzing} Boolean functions.
This class, introduced in \cite{Kauffman-1969}, is defined as follows.

>>>>

Rsearch on the symmetry properties of Boolean
functions has received a lot of attention from the
logic design and automated synthesis communities. 
(Additional discussion on this is provided in Section~\ref{sse:related}.)
In this paper, we focus on the symmetry properties of
a class of Boolean functions (called \textbf{nested canalyzing functions})
which are used to model biological phenomena.
To define this class, we start with a simpler
class of functions, called \textbf{canalyzing} Boolean functions.
This class, introduced in \cite{Kauffman-1969}, is defined as follows.

### 2019-06-06 dmtcs_submission.d/symmetry_properties.tex
ssr: creating the version for DMTCS

\section{Symmetry of Nested Canalyzing\newline Functions}
\label{sec:ncf_and_symmetry}

@@

\subsection{Symmetric Pairs of Variables in an NCF:\newline 
A Characterization and its Applications}
\label{sse:ncf_strong_sym}

@@

\subsection{Testing Whether an $r$-Symmetric Function\newline is an NCF}
\label{sse:rsym_to_ncf}

@@

Hence, the number of Boolean functions with $n$ variables that
are both strongly asymmetric and NCFs is equal to \\ 
$2 \times (n!/2) \times 2^{n-1}$ ~=~ $n!\,2^{n-1}$.  \QED

>>>>

\section{Symmetry of Nested Canalyzing Functions}
\label{sec:ncf_and_symmetry}

@@

\subsection{Symmetric Pairs of Variables in an NCF:
A Characterization and\newline its Applications}
\label{sse:ncf_strong_sym}

@@

\subsection{Testing Whether an $r$-Symmetric Function is an NCF}
\label{sse:rsym_to_ncf}

@@

Hence, the number of Boolean functions with $n$ variables that
are both strongly asymmetric and NCFs is equal to 
$2 \times (n!/2) \times 2^{n-1}$ ~=~ $n!\,2^{n-1}$.  \QED
